### 2022-05-24 paper.Rmd
prmisc not needed in current manuscript

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
library("prmisc") # remotes::install_github("m-Py/prmisc")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

>>>>

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")
